---
title       : Predicting with mpg
subtitle    : Prediction other car properties based on miles per gallon 
author      : Sprixx
job         : Course Project
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- bg:lightblue

## The need to predict with mpg

Welcome to the pitch of my shiny app.

A lot of properties of a car are correlated with the miles per gallon variable.

It can therefore be interesting to investigate the effect of miles per gallon on these variables individually.

Questions like: how much more or less horsepower does a car have which has 30 miles to the gallon instead of 20 miles to the gallon ceteris paribus are interesting questions when buying a car.

This app makes it fast, easy and most of all fun to investigate this kind of linear relationships.

--- bg:lightblue

## The shiny application input

The first thing that should be selected in the app is the variable which you want to predict with mpg, using the drop down menu.
The application next fits a linear regression line between mpg and your selected variables, plots this and provides the coefficients of the regression. Note that the color depends on the number of cylinders. 

Next you are able to make a prediction by setting mpg using the slider bar. The predicted value is next shown based on the coefficients of the regression model and is also visible in the plot: the red dot and the vertical and horizontal line in this red dot.

If you for example select the wt (weight) variable and set mpg equal to 25 the following is predicted for weight:
```{r}
coef(lm(mtcars$wt~mtcars$mpg))[1]+coef(lm(mtcars$wt~mtcars$mpg))[2]*25
```

--- bg:lightblue

## The calculation and output
This result can also be seen in the plot using the following code:

```{r,echo=TRUE,fig.height=3,fig.width=12}
plot(mtcars[,c(1,6)],col = mtcars$cyl, pch = 20,cex=2)
        abline(lm(mtcars[, c("wt")]~mtcars[, c("mpg")]))
        abline(v=25)
        abline(h=(coef(lm(mtcars$wt~mtcars$mpg))[1]+coef(lm(mtcars$wt~mtcars$mpg))[2]*25))
        points(25,(coef(lm(mtcars$wt~mtcars$mpg))[1]+coef(lm(mtcars$wt~mtcars$mpg))[2]*25),col="red",pch=20,cex=4)
```

--- &radio

## Final Questions

Based on the previous plot, should I buy a heavy or light car?

1. A light car

2. A heavy car

3. _This depends on the looks of the car, the performance of the car, the price of the car, the amount of money I have, the number of kids I can fit, the brand, and much more. Miles per gallon only is a small portion of the decision about buying a car_

*** .hint How do you buy a car?

*** .explanation It is an illustrative simple shiny app, and will not be very applicable in real life. Secondly, the used data set is very old.

